\chapter*{Abstract}

	\noindent Microwave Imaging is an important nondestructive and noninvasive testing and evaluating technique with many applications in diverse areas, such as medical imaging, security screening, remote sensing, among others. The technique is based on an Electromagnetic Inverse Scattering Problem where the electric properties of a medium are recovered through scattered field measurements. Besides being an ill-posed problem, it is also nonlinear and multimodal. There are several numerical methods for solving the problem and they can be classified into qualitative and quantitative ones. The latter is also classified into deterministic and stochastic methods. This thesis presents a novel quantitative deterministic approach for microwave imaging using surrogate model-assisted algorithms. The objective is to address the challenges of the inverse problem by considering the qualitative image recovered by the Orthogonality Sampling Method and transforming it into a two-dimensional optimization problem. The proposed method focuses on optimizing the contrast estimation and the threshold operation to minimize the data equation error. The thesis introduces three formulations based on Evolutionary Algorithms and two ones based on Descent Methods, providing a range of options for solving the optimization problem. In addition, a new framework is proposed for the development and testing of algorithms in microwave imaging. The framework includes a comprehensive package called \textit{eispy2d}, which offers functionalities such as test set generation with parameter control, a collection of performance indicators (including two novel indicators), and support for statistical comparison of different algorithms. The results of the experiments demonstrate the effectiveness of the proposed methods. In weak scatterer scenarios, the surrogate model-assisted algorithms were able to recover images that were comparable to those obtained by traditional methods, while achieving similar runtimes. Moreover, in more challenging scenarios where traditional methods failed, the proposed algorithms showed consistent results in terms of image recovery.
	
	\vspace{5mm}
	
	\noindent\textbf{Keywords}: microwave imaging; inverse problems; surrogate model-assisted algorithms; evolutionary algorithm; descent methods; open-source package.
	
	\thispagestyle{empty}
	