\newpage

\chapter*{Acknowledgements}

	I would like to express my deepest gratitude to my family for their unwavering support throughout my academic journey. I am thankful for my dad. I still remember when he used to double check my homework every morning when I was a kid. I am thankful my mom. I still remember you waking me up and putting on clothes to go to school. I am thankful for my sister. I think I would never know that I could to go college and even studying at UFMG if she had not did it before. I am grateful for my brother. I will never forget that you gave me your computer so I could study at university. Your love, encouragement, and understanding have been the pillars that have sustained me during the challenges and triumphs of this thesis.
	
	I am especially grateful to Fernanda, who will be my wife in some days. There is no way to talk about this doctorate without thinking of you. From the beginning to end, you have been with me. Your companion and your kindness have been instrumental in allowing me to dedicate the time and energy necessary to complete this research. I am truly blessed to have her by my side.
	
	I extend my heartfelt appreciation to my advisor, Lucas S. Batista. More than 10 years since I first showed up in your room and you gave the opportunity for a student that still did not know what a gradient or contour plot were. You truly shaped me, as a researcher and professor.
	
	I am also thankful for my co-advisor, Ricardo Adriano. You always were really patient with me even when I did not deserve it. Thank you for friendship and every effort when I had questions. Your expertise has been crucial in expanding my understanding.
	
	I will always be grateful to my friends from ABU for their camaraderie, support, and talks. Their friendship has shaped me a lot through the years and I hope it will always be like this.
	
	Finally, I would like to express my sincere appreciation to Presidents Luiz Inácio Lula da Silva and, specially, Dilma Rousseff for their commitment to education and scientific research. Their vision and policies have played a crucial role in creating a conducive environment for academic pursuits, including my own. I am a legacy of what they believed that education could be.
	
	To all those who have supported me in ways seen and unseen, thank you. This thesis would not have been possible without your unwavering support, encouragement, and belief in my abilities.
	
	\thispagestyle{empty}